RD design analysis

### 2024-01-05 analysis/RD design analysis.Rmd
Rename RD design analysis.Rmd to analysis/RD design analysis.Rmd

```{r}
control_variables <- c(
  "jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park", 
  "area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident",
  "L_jiadian", "L_kind", "L_hotel", "L_shop_mall", "L_museum", "L_old", "L_ktv", "L_mid", "L_prim", "L_west_food", "L_super", "L_sub", "L_park",
  "pm25", "pop", "light",
  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes",
  "density", "lianjia_5", "other_5", "ln_lead", "ln_watch_people"
)
```

```{r}
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$density, 
       c = 0.2, p =1,  nbins = 20, 
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.
```{r}
h = 0.151
cutoff = 0.5
running_var = panel_data$nearest_store_distances

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, p = 1, nbins = 20, 
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$density, 
                   c = 0.2, covs = panel_data[, control_variables],
                   p = 1) # first using default clustering
```

@@

>>>>

```{r}
control_variables <- c(
  "jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park", 
  "area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident",
  "pm25", "pop", "light",
  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people"
)
```

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                   c = 0.41, covs = panel_data[, control_variables],
                   p = 1) # first using default clustering
```

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                   c = 0.41,
                   p = 1) # first using default clustering
```

@@

note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.

```{r}
h = 0.095
cutoff = 0.41
running_var = panel_data$nearest_store_distances

par(mfrow=c(3,1))
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

checkings:

1. Donut Hole: Exclude observations close to the cutoff and estimate the effect with the remaining data. If the discontinuity persists despite the absence of data around the cutoff, this provides evidence against a model misspecification.
2. Mccrary (2008) test: Conduct a McCrary density test to check if there is a discontinuity in the density of the running variable at the cutoff. A significant discontinuity may suggest manipulation or sorting around the cutoff.
3. Placebo test: If you have pre-treatment covariates, you can test whether these covariates also jump at the cutoff. If they do, this might suggest manipulation or a violation of the RD design assumptions. If they don’t, it strengthens the case for a true treatment effect.

```{r}
cutoff
donut_width <- 0.011
panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                         x = panel_data_donut$nearest_store_distances, 
                         c = cutoff,
                        p = 1, h = 0.066, b = 0.135)
pander(cbind(result_donut$coef, result_donut$pv))
print(result_donut)
```

```{r}
donut_width <- 0.015
panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                         x = panel_data_donut$nearest_store_distances, 
                         c = cutoff,  covs = panel_data_donut[, control_variables],
                        p = 1, h = 0.095, b = 0.185)
pander(cbind(result_donut$coef, result_donut$pv))
print(result_donut)
```

```{r}

library(rdd)

# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
```

```{r}
library(rdd)

# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.095, verbose = TRUE, plot = FALSE)
```

Conducting placebo test

```{r}
# using the same bandwidth
unrelated_result <- rdrobust(y = panel_data$ln_negotiation_period, 
                             x = panel_data$nearest_store_distances, c = 0.41, h = 0.066, b = 0.135)
print("Placebo test with unrelated outcome:")
print(unrelated_result)
pander(cbind(unrelated_result$coef, unrelated_result$pv))
```
